\documentclass[11pt,a4paper]{article}
\usepackage[inline]{enumitem}
\usepackage{titlesec}
\titleformat{\subsection}[block]{\Large\bfseries\filcenter}{}{1em}{}
\usepackage[nohead,nofoot,hmargin=2cm,vmargin=1cm]{geometry}
\usepackage{tabularx}
\usepackage{wasysym}
\usepackage{marvosym}
\usepackage{hyperref}
\usepackage{mathptmx}
\usepackage{xcolor}
\hypersetup{
    colorlinks,
    linkcolor={red!50!black},
    citecolor={blue!50!black},
    urlcolor={blue!80!black}
}
\usepackage{titlesec}
\titlespacing*{\subsection}{0pt}{0pt}{0pt}

\setlength\parindent{0pt}
%course/job title ; employer/institution ; dates
\newcommand{\centry}[3]{\paragraph{#1} \textit{#2}%
\hfill#3\\[2pt]}
%
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parskip}{1em}
\begin{document}

\begin{tabularx}{\linewidth}{XX}
  \begin{flushleft}
    {\large MAX RUDIN}\\[\baselineskip]
    \href{https://www.linkedin.com/in/maxrudin/}{https://www.linkedin.com/in/maxrudin}
  \end{flushleft}
&
  \begin{flushright}
    \href{tel:+447593353993}{+44 7593 353993}\\
    \href{mailto:max@rudin.co.uk}{max@rudin.co.uk}\\[\baselineskip]
    2 Sedley Taylor Road,\\
    Cambridge, CB2 8PW
  \end{flushright}
\end{tabularx}

\hrule

\subsection*{Summary}

A motivated and organised Environmental Science final year student currently
studying at the University of the West of England. Due to my hospitality
experience, I excel working under pressure and I am a good multitasker. I
always maintain a positive attitude and believe I can bring energy and charisma
into my work life. I can work well both in a team and on my own as I am
independent and a self-starter. At university I was a sports team captain leading my 
club to several national championships. I had to lead training sessions to up to 50 people, 
be responsible for recruiting new members, organising fixtures, accommodation and travel.


\subsection*{Education}


\centry{BSc(Hons) Environmental Science}{University of the West of
  England}{2017--2020}

I achieved the highest course marks in first year and was awarded the Ryan Lee
Memorial Award and was on the Dean's List. My overall grade for the first year
was a 1st with (73\%). In the second year my overall grade was 2:1 (63\%) and am
predicted a 2:1 for my third year.

Example modules taken:
\setlist[description]{font=\normalfont\itshape\space}
\begin{description}
\item[Research Dissertation Project (64\%)] I studied the changes in Arctic
  lakes by using satellite data within ArcGIS. I also compared accuracies of
  different land use classification methods from data acquired from different
  satellites.  
\item[Environmental Microbiology (69\%)] I developed laboratory skills, studied
  bioremediation, wastewater treatment processes, microbial ecology and
  biotechnology. Developed my understanding of alternative energy production
  methods by reviewing and writing a report on microbial fuel cells.
\item[Atmosphere and Climate (71\%)]  I gained practical experience of a range of
  analytical and modelling techniques utilised in climate science, gained
  experience of atmospheric modelling and understood and evaluated the risks
  associated with air pollution and climate change.
\item[Remote sensing and GIS (69\%)] I imported environmental data into GIS
  packages, applied GIS to the presentation and analysis of remotely sensed
  data. For example, mapping the theoretical flood heights and creating an
  ArcGIS StoryMaps presentation to show the data.  
  \item[Energy Technologies (Awaiting result)] where I
  critically assessed different energy technologies with respect to climate
  mitigation and the socioeconomic challenges they face. I assessed the future
  of the UK’s energy production especially regarding the target of reaching net
  zero carbon emissions by 2050.  
  \item[Resource Security and Sustainability (72\%)] where I
  developed my understanding of environmental policies and concepts such as
  circular economy as well as experience in environmental modelling. 
\item[Ecology and Ecosystem Protection (61\%)] I developed field skills by, for
  example, undertaking a Phase 1 habitat survey. Performed statistical analysis
  on environmental data using R.
\end{description}


\centry{BSc Games Technology}{Bournemouth University}{2014--2016}
Awarded a Certificate of Higher Education in Games Technology. Withdrew after 
realising I wanted to pursue a degree in Environmental Science.

\centry{A Levels}{Hills Road Sixth Form College, Cambridge} {2011--2013}
\begin{center}
  \begin{tabular}{llll}
    Maths & B & Physics & C \\
    Biology & D  & Chemistry (AS Level) & C\\
  \end{tabular}
\end{center}

\centry{GCSEs}{The Netherhall School, Cambridge}{2006--2011} 
10 GCSEs grades A*-C:
\begin{center}
  \begin{tabular}{llll}
    Chemistry & A* & Geography & A \\
    Biology& A & Maths& A \\
    French& A & English Language& B \\
    PE& B &  History& B\\
    English Literature& B & Physics& B\\
  \end{tabular}
\end{center}

\subsection*{Employment}

\centry{Floor Team Member}{Wasabi Sushi \& Bento}{Summer 2017 \& 2018}

Experience includes working in a fast-paced environment as part of a team whilst 
maintaining a high level of customer service. Working with a high volume of 
customers and therefore completing tasks and solving problems at a high speed. 

\centry{Cycle Courier}{Deliveroo}{Summer 2016}

Experience includes: Interacting with clients to solve any issues they had on 
the spot. Working to tight schedules, while also being careful. 


\centry{Shop Floor Assistant}{Waitrose}{November 2013--February 2014}

Experience includes: Working as a team whilst sticking to deadlines. 
Keeping organised and prioritising the workload.

\subsection*{Additional Information}

I am a student member of the Institute of Environmental Sciences.

I have participated in Ultimate Frisbee teams throughout university and I am a keen runner.

Qualifications:
\begin{itemize}
  \item Level 3 Emergency First Aid at Work    
  \item Level 1 UKU Ultimate Frisbee Coach
  \item SSI Open Water Diver
\end{itemize}

\end{document}

